Generate Real and Pseudo-absences

### 2023-12-29 scripts/download_dependent_variables.Rmd
found number of cases where species detected on plot before and after fire

thinned <- lapply(splicies, ONEperCELL)
thinned <- bind_rows(thinned)
st_write(thinned, '../data/raw/occurrence/thinned/thinned_occurrences.shp', append = F)
repeated_occurrences <- lapply(splicies, multiplesPERcell)
repeated_occurrences <- purrr::discard(repeated_occurrences, ~nrow(.) < 2)
repeated_occurrences <- bind_rows(repeated_occurrences)
st_write(repeated_occurrences, '../data/raw/occurrence/repeated/repeated_occurrences.shp', append = F)

@@

```{r Create consensus presence records}

>>>>

thinned <- lapply(splicies, ONEperCELL)
thinned <- bind_rows(thinned)
# st_write(thinned, '../data/raw/occurrence/thinned/thinned_occurrences.shp', append = F)
repeated_occurrences <- lapply(splicies, multiplesPERcell)
repeated_occurrences <- purrr::discard(repeated_occurrences, ~nrow(.) < 2)
repeated_occurrences <- bind_rows(repeated_occurrences)
st_write(repeated_occurrences, '../data/raw/occurrence/repeated/repeated_occurrences.shp', append = F)

@@

```{r Create consensus presence records 2, eval = F}

### 2023-12-29 scripts/generate_absences.Rmd
found number of cases where species detected on plot before and after fire

@@

recs <- bind_rows(absences, presences) %>% 
  group_by(taxon) %>% 
  mutate(ID = 1:n())

collinear_probs <- read_rds( '../results/bioclim_VIF_PA_drop.rda')
bio <- usdm::exclude(bio, collinear_probs)

@@

```{r remove pseudo absences in presence niche space}

set.seed(27)

cn <- names(bio)
# splicies <- split(recs, f = recs$taxon)
lapply(splicies, lda_PA_dropper, path = '../results/lda/', col_names = cn)

which(names(splicies)[130] == 'Dudleya cymosa')
# need to restart on record 130, 
# which is Dudleya cymosa ssp. cymosa, and which should be subsumed into Dudleya cymosa!
# the problem was that a variable displayed 0 variance because there were only 2 records!!!
```

>>>>

collinear_probs <- read_rds('../results/bioclim_VIF_PA_drop.rda')
bio <- usdm::exclude(bio, collinear_probs)

@@

recs <- bind_rows(absences, presences) %>% 
  mutate(taxon = str_replace(taxon, 'Dudleya cymosa ssp. cymosa', 'Dudleya cymosa')) %>% 
  group_by(taxon) %>% 
  mutate(ID = 1:n())

@@

```{r remove pseudo absences in presence niche space, eval = F}

set.seed(27)
cn <- names(bio)
splicies <- split(recs, f = recs$taxon)

lapply(splicies, lda_PA_dropper, path = '../results/lda/', col_names = cn)
```
